Competing Constructions for German Measure Phrases

### 2017-03-18 Latex/article.tex
swapping more graphics, final

\begin{figure}[h]
\centering
\includegraphics[width=0.9\textwidth]{figures/corpus/04_glmm_fixef.pdf}
\caption{Fixed effects in GLMMs for Masculine\slash Neuter and Feminine with 95\% bootstrapped confidence intervals (1,000 replicates)}
\label{fig:glmmfixef}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.9\textwidth]{figures/corpus/04_glmm_fixef_firstlevel}
\caption{Estimated first-level effects in GLMMs for Masculine\slash Neuter and Feminine}
\label{fig:glmmfixef}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.9\textwidth]{figures/corpus/04_glmm_fixef_secondlevel_kind}
\caption{Estimated second-level effects for kind lemmas in GLMMs for Masculine\slash Neuter and Feminine}
\label{fig:glmmfixef}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.9\textwidth]{figures/corpus/04_glmm_fixef_secondlevel_measure}
\caption{Estimated second-level effects for measure lemmas in GLMMs for Masculine\slash Neuter and Feminine}
\label{fig:glmmfixef}
\end{figure}
